Order Reduction and MILP Models for Real-Time DNN Robustness Certification \\ Supplementary Material

### 2025-09-01 AAAI2026/experiments.tex
update the new test for pipe system
TIMES REMOVED

\begin{table}[b!]
	\centering
	\begin{tabular}{||l|c|c|c||}\hline\hline
		model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
	Classical, $50 \times 2$ &    $.320$ &  $.320$ & $.017$ 
    \\\hline
	ITNE, $50 \times 2$ &    $.042$ &  $.037$ & $.022$
	\\ \hline
    2v model, $50 \times 2$ &    {\bf .040} &  $.037$ &  $.018$ 
    \\\hline \hline
    Classical, $100 \times 2$ &  .186  &  $.022$ & $.022$ 
    \\\hline
	ITNE, $100 \times 2$ &    $.045$ &  $.023$ & .023
    \\\hline
	2v model, $100 \times 2$&     {\bf .042} &  $.023$ &   .023 
    \\\hline \hline
	\end{tabular}
	\caption{Comparison of the classical encoding, ITNE and our "2v" model on the pipe system with a fixed timeout of 1000s, with either $50 \times 2$, 
    or the full $100 \times 2$ binary variables.}
    \label{table.classical}
\end{table}

@@

Table \ref{table.classical}, $50 \times 2$, confirms that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model, when 50 variables use LP relaxation. Adding explicitly LP relaxation constraints of Eq. (3) from \cite{ITNE} recovers most but not all the bound of the "2v" model.

Further, even using a fully accurate model with all $100 \times 2$ variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation. Again, 
Eq. (3) from \cite{ITNE} recovers most but not all the accuracy of the "2v" model.
Overall, the "2v" model produces better bounds, even with short time-outs, despite its higher complexity.

@@

	\begin{table}[h!]
		\centering
	\begin{tabular}{||l||c|c|c||}\hline\hline
		model &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
		1v, $500 \times 1$ & {\bf 14.97} & $.845$ & $.009$ \\\hline 
		3v, $500 \times 3$ & $17.66$ & $.813$ & {\bf .518} \\\hline 
	    2v, $500 \times 2$ & $16.49$ & n/a & n/a \\\hline\hline	 
	\end{tabular}
	\caption{Bounds on $\beta^{.5}_{6,8}$ 
	obtained by the "1v", "3v" and "2v" models 
	on the {\bf full dimension} MNIST DNN, 
	for timeouts of $14400$s, when all 500 ($\times 1$, $\times 2$, $\times 3$) variables are binary.}
	\label{table.mnist}
\end{table}

@@

\begin{figure*}[t!]
	\centering
\includegraphics[scale=0.6]{image.png} \hspace{1.5cm}
\includegraphics[scale=0.6]{perturb.png}
\caption{An improbable image for MNIST and its perturbation ($L1$-difference of $.5$ in a unique pixel at x=14, y=8 from top) with maximal $\beta^{.5}_{6,8}=0.518$, as obtained by the "3v" $500 \times 2$ model in {\bf full 784 dimension} image space.}
\label{fig3}
\end{figure*}

\begin{figure*}[t!]
	\centering
\includegraphics[scale=0.5]{redimage.png} \hspace{1.5cm}
\includegraphics[scale=0.5]{redperturb.png}
\caption{An image for MNIST and its perturbation from the {\bf 20-dimension reduced space} with maximal $\beta^{.5}_{6,8}=.084$, as obtained by the "2v" $500 \times 2$ model.}
\label{fig4}
\end{figure*}

\begin{table}[b!]
	\centering
	\begin{tabular}{||l||c|c|c||}\hline\hline
		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ \\\hline \hline
%1v, $400 \times 1$ & $1.414$ &  $.691$ & $.010$ \\\hline 
%3v, $400 \times 3$ & $1.186$ & $.600$ & $.003$ \\\hline 
%2v, $400 \times 2$ & $1.274$ & $.566$ & $.002$ \\\hline\hline

@@

1v, $500 \times 1$ & $1.412$ & $.161$ & .057 \\\hline 
3v, $500 \times 3$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
2v, $500 \times 2$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline

	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models 
	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf 20 dimension} reduced order MNIST DNN, for timeout of 14400s, where 
	all %400, 475,  or 
	500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
	\label{table.reduced}
\end{table}

@@

\begin{table}[b!]
	\begin{tabular}{||l||c|c|c|c||}\hline\hline
		model &    $L_1\leq 0.5$ & $L_1\leq 1$ & $L_1\leq 1.5$ &  $L_1\leq 2$ \\\hline \hline
		1v, $500\times1$ & $80 \%$ & $32\%$ & $7\%$ & $0\%$ \\\hline
		3v, $500 \times 3$ & {\bf 86 \%} & {\bf 53\%} & {\bf 20\%} & {\bf 4\%} \\\hline
		2v, $500 \times 2$ & 84\% & 51\% & 16\% & {\bf 4\%} \\\hline \hline
	\end{tabular}
	\caption{Percentage of images certified robust in real-time 
	using the computed $(\beta^{.5}_{i,j})_{i < j \leq 10}$ 
	by the "1v", "3v" and "2v" models, for different values of $L_1$-perturbations.}
    \label{table.cert}
\end{table}

@@

	\begin{figure*}[t!]
\includegraphics[scale=0.5]{deform.png} \hspace{0.8cm}
\includegraphics[scale=0.5]{strain.png}
\caption{2 slightly different deformations and their associated quite different strain as obtained by the "2v" $100 \times 2$ model.}
\label{fig5}
\end{figure*}

@@

	\begin{table}[h!]
	\begin{tabular}{||l||c|c|c|c||}\hline\hline
		model &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ &  Time(s) \\\hline \hline
		1v, $100 \times 1$ &     {\bf .0356} &  $.0356$ & $.0191$ &  1000 \\\hline
		3v, $100 \times 3$&     .0414 &  .0254 &  .0166 &  1000 \\\hline
		2v, $100 \times 2$&     .0418 &  .0229 &   {\bf .0229} &  1000 \\\hline \hline
		%3v, $97 \times 3$&      ?? &  ?? &  ?? & 14440 \\\hline
		3v, $100 \times 3$&      {\bf .0350} &  .0272 &  .0216 & 14440 \\\hline
		%2v, $97 \times 2$&     ?? &  ?? &   ?? & 14440 \\\hline
		2v, $100 \times 2$&     .0360 &  .0236 &    {\bf .0236} & 14440 \\\hline \hline
		3v, $100 \times 3$&     {\bf .0329} &  .0277 &  .0165 & 72000 \\\hline
		2v, $100 \times 2$&     .0337 &  .0245 &  {\bf .0245} & 72000 \\\hline\hline
	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with timeouts of 1000s, 14440s and 72000s, where all 100 ($\times 1, \times 2,\times 3$) neurons use binary variables.}
	%L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}
	\label{table.pipe}
\end{table}

>>>>

\begin{table}[b!]
	\centering
	\begin{tabular}{||l|c|c|c||}\hline\hline
		model, nbr binary var &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
	Classical, $100$ &    $.320$ &  $.320$ & $.017$ 
    \\\hline
	ITNE, $100$ &    $.042$ &  $.037$ & $.022$
	\\ \hline
    2v model, $100$ &    {\bf .040} &  $.037$ &  $.018$ 
    \\\hline \hline
     2v model New, $100$ &    {\bf .039} &  $.029$ &  $.020$ 
    \\\hline \hline
    Classical, $200$ &  .186  &  $.022$ & $.022$ 
    \\\hline
	ITNE, $200$ &    $.045$ &  $.023$ & .023
    \\\hline
	2v model, $200$&     {\bf .042} &  $.023$ &   .023 
    \\\hline \hline
	\end{tabular}
	\caption{Comparison of the classical encoding, ITNE and our "2v" model on the pipe system with a fixed timeout of 1000s, with either $100$, 
    or the full $200$ binary variables.}
    \label{table.classical}
\end{table}

@@

Table \ref{table.classical}, $100$, confirms that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model, when 50 variables use LP relaxation. Adding explicitly LP relaxation constraints of Eq. (3) from \cite{ITNE} recovers most but not all the bound of the "2v" model.

Further, even using a fully accurate model with all $100$ variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation. Again, 
Eq. (3) from \cite{ITNE} recovers most but not all the accuracy of the "2v" model.
Overall, the "2v" model produces better bounds, even with short time-outs, despite its higher complexity.

@@

	\begin{table}[h!]
		\centering
	\begin{tabular}{||l||c|c|c||}\hline\hline
		model, nbr binary var &        Bound $\downarrow$ &  Sol. &      Worst-Case $\uparrow$ \\\hline \hline
		1v, $500$ & {\bf 14.97} & $.845$ & $.009$ \\\hline 
		3v, $1000$ & $17.66$ & $.813$ & {\bf .518} \\\hline 
	    2v, $1000$ & $16.49$ & n/a & n/a \\\hline\hline	 
	\end{tabular}
	\caption{Bounds on $\beta^{.5}_{6,8}$ 
	obtained by the "1v", "3v" and "2v" models 
	on the {\bf full dimension} MNIST DNN, 
	for timeouts of $14400$s, when all 500 / 1000 variables are binary.}
	\label{table.mnist}
\end{table}

@@

\begin{figure*}[t!]
	\centering
\includegraphics[scale=0.6]{image.png} \hspace{1.5cm}
\includegraphics[scale=0.6]{perturb.png}
\caption{An improbable image for MNIST and its perturbation ($L1$-difference of $.5$ in a unique pixel at x=14, y=8 from top) with maximal $\beta^{.5}_{6,8}=0.518$, as obtained by the "3v" model in {\bf full 784 dimension} image space.}
\label{fig3}
\end{figure*}

\begin{figure*}[t!]
	\centering
\includegraphics[scale=0.5]{redimage.png} \hspace{1.5cm}
\includegraphics[scale=0.5]{redperturb.png}
\caption{An image for MNIST and its perturbation from the {\bf 20-dimension reduced space} with maximal $\beta^{.5}_{6,8}=.084$, as obtained by the "2v" model with $1000$ binary variables.}
\label{fig4}
\end{figure*}

\begin{table}[b!]
	\centering
	\begin{tabular}{||l||c|c|c||}\hline\hline
		model, nbr binary var &        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ \\\hline \hline
%1v, $400 \times 1$ & $1.414$ &  $.691$ & $.010$ \\\hline 
%3v, $400 \times 3$ & $1.186$ & $.600$ & $.003$ \\\hline 
%2v, $400 \times 2$ & $1.274$ & $.566$ & $.002$ \\\hline\hline

@@

1v, $500$ & $1.412$ & $.161$ & .057 \\\hline 
3v, $1000$ & {\bf 1.137} & $.103$ & $.065$\\\hline 
2v, $1000$ &  $1.182$ & $.084$& {\bf .084}  \\\hline\hline

	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models 
	to obtain bounds on $\beta^{.5}_{6,8}$ on the {\bf 20 dimension} reduced order MNIST DNN, for timeout of 14400s, where 
	all %400, 475,  or 
	neurons use 500 / 1000 binary variables.}
	\label{table.reduced}
\end{table}

@@

\begin{table}[b!]
	\begin{tabular}{||l||c|c|c|c||}\hline\hline
		model, nbr &    $L_1\leq 0.5$ & $L_1\leq 1$ & $L_1\leq 1.5$ &  $L_1\leq 2$ \\\hline \hline
		1v, $500$ & $80 \%$ & $32\%$ & $7\%$ & $0\%$ \\\hline
		3v, $1000$ & {\bf 86 \%} & {\bf 53\%} & {\bf 20\%} & {\bf 4\%} \\\hline
		2v, $1000$ & 84\% & 51\% & 16\% & {\bf 4\%} \\\hline \hline
	\end{tabular}
	\caption{Percentage of images certified robust in real-time 
	using the computed $(\beta^{.5}_{i,j})_{i < j \leq 10}$ 
	by the "1v", "3v" and "2v" models, for different values of $L_1$-perturbations.}
    \label{table.cert}
\end{table}

@@

	\begin{figure*}[t!]
\includegraphics[scale=0.5]{deform.png} \hspace{0.8cm}
\includegraphics[scale=0.5]{strain.png}
\caption{2 slightly different deformations and their associated quite different strain as obtained by the "2v" model with $200 $ binary variable.}
\label{fig5}
\end{figure*}

@@

	\begin{table}[h!]
	\begin{tabular}{||l||c|c|c|c||}\hline\hline
		model, nbr&        Bound$\downarrow$ &  Sol. &      Worst-Case$\uparrow$ &  Time(s) \\\hline \hline
		1v, $100$ &     {\bf .0356} &  $.0356$ & $.0191$ &  1000 \\\hline
		3v, $200$&     .0414 &  .0254 &  .0166 &  1000 \\\hline
		2v, $200$&     .0418 &  .0229 &   {\bf .0229} &  1000 \\\hline \hline
		%3v, $97 \times 3$&      ?? &  ?? &  ?? & 14440 \\\hline
		3v, $200$&      {\bf .0350} &  .0272 &  .0216 & 14440 \\\hline
		%2v, $97 \times 2$&     ?? &  ?? &   ?? & 14440 \\\hline
		2v, $200$&     .0360 &  .0236 &    {\bf .0236} & 14440 \\\hline \hline
		3v, $200$&     {\bf .0329} &  .0277 &  .0165 & 72000 \\\hline
		2v, $200$&     .0337 &  .0245 &  {\bf .0245} & 72000 \\\hline\hline
	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models on the pipe system with timeouts of 1000s, 14440s and 72000s, where all neurons use 100 / 200 binary variables.}
	%L1 corresponds to $3.9$ or $4$, and results should be the sum of 10 pixels, so around 10 times higher values.}
	\label{table.pipe}
\end{table}
